---
title: "Social Survey 2010"
author: "Joseph Nielsen"
date: "Fall 2018"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyvertse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

Use the data from the 2010 general social survey to explore whether belief in continental drift (condrift), views on capitol punishment (cappun), and race (race) are independent of each other.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

We used the data from alldata to get our statistics. Then we ran multipe tests to analyze the variables given. We used a bar graph for each of the tests; Race vs condrift, rave vs cappun, and cappun vs condrift. Then we ran many statstical tests. We did a basic statstical test on each and a Chi-Square test on each. This gives us enough infoprmation to come to a conclusion ofr each qeustion.  
#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
alldata <- read.csv(file="gss2010.csv", header=TRUE)
#names(alldata)
```


## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
barchartGC(~race+condrift, data=alldata, type = "percent") 
```


```{r}
barchartGC(~race+cappun, data=alldata, type = "percent") 
```

```{r}
barchartGC(~condrift +cappun, data=alldata, type = "percent")
```

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r} 
tab = xtabs(~race+condrift, data=alldata)
rowPerc(tab)
```


```{r}
tab2 = xtabs(~race+cappun, data=alldata)
rowPerc(tab2)
```

```{r}
tab3 = xtabs(~condrift+cappun, data=alldata)
rowPerc(tab3)
```

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
chisqtestGC(~race+condrift, data=alldata, graph = TRUE)
```

```{r}
chisqtestGC(~race+cappun, data=alldata, graph = TRUE)
```

```{r}
chisqtestGC(~condrift+cappun, data=alldata, graph = TRUE)
```

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Race Vs Condrift  
  Just from looking at the bar charts one can see that most whites and other believe that continantial drift is true. While in the black section a higher precent of people  that believe that continantial dirft is false. Then looking at the basic statstical results it shows that 23.3% black people found continantail drift to be false while less than 10% found it false in the other two races. The Chi-square calculated value is greater than the chi-square critical value, then we reject our null hypothesis. Meaning that there is a relationship between race and condrift.  
  
Race VS Cappun  
  The race that favors capital punishment the most is white people at 72.7%. While black people oppose it the mostbecause on;y 46.8 favor it. While others is split about with 56.5% favor it. The Chi-square calculated value is greater than the chi-square critical value, then we reject our null hypothesis. Meaning that there is a relationship between race and Cappun. 
    
Condrift Vs Cappun  
  I dont really see any relationships here because either way if you think continantial drift is true or false about 66% favor capital punishment either way so i dont know what to take from this. Chi-square calculated value is less than the chi-square critical value, then we accept the null hypothesis. Meaning that there is no relationship between the two.
  
    